Parsing medial prefrontal cortex: A joint meta-analytic and graph-theoretic approach.

### 2018-08-27 Manuscript/Manuscript.Rmd
Working on methods and discussion a bit

  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011). However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

@@

>>>>

  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011). However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

@@

For clinical implications, see Hiser & Koenigs 2018. In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC. It would be more interesting to identify the repercussions to damage in mPFC per individual. They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment. The refinement of the technique is thus coupled to being able to identify personalized functional topologies. They list a number of results related to mPFC functional connectivity too. In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse. (note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)
